Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-09-29 3_review-responses/V2_review_responses/Reviewer #1 Response.txt

Thank you for your comments. I will enclose them in hyphens and respond below that section for each comment. I will also include quotes from Reviewer #5 where necessary, using '>>>' before it.

In summary, we added two more layers to our study. We divided the data in price ranges, and we added automatic adjective + noun pairing counts, by using dependency parsing and part of speech tagging.

------------
1. Comment #3 from Reviewer #3
It is not a deal breaker. However, I am with Reviewer #3 that the hypotheses of this study bring much value to the body of our knowledge. In the sense that this study took an exploratory approach (i.e., data mining), hypothesis testing may not be ideal to achieve the research goal.

>>>Comment #3 from Reviewer #3
>>>"#3 - Literature review
    *  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them. 
------------

After some thought, we do agree that the hypotheses are able to be removed without altering the objective of the paper at all. However we still view value in using these questions as a statement of the paper's objective and to better structure and showcase our results. Because of this, we changed them to "Research Questions". Research questions 1a and 1b will relate to the how the customers reach to omotenashi and how they differentiate from each other, while research questions 2a and 2b will relate to hard and soft attributes and how the management decisions can impact future improvement in customer satisfaction.

### 2020-09-29 3_review-responses/V2_review_responses/Reviewer_Responses_all.txt

Reviewer #1 Response

Thank you for your comments. I will enclose them in hyphens and respond below that section for each comment. I will also include quotes from Reviewer #5 where necessary, using '>>>' before it.

------------
1. Comment #3 from Reviewer #3
It is not a deal breaker. However, I am with Reviewer #3 that the hypotheses of this study bring much value to the body of our knowledge. In the sense that this study took an exploratory approach (i.e., data mining), hypothesis testing may not be ideal to achieve the research goal.

>>>Comment #3 from Reviewer #3
>>>"#3 - Literature review
    *  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them. 
------------

After some thought, we do agree that the hypotheses are able to be removed without altering the objective of the paper at all. However we still view value in using these questions as a statement of the paper's objective and to better structure and showcase our results. Because of this, we changed them to "Research Questions". Research questions 1a and 1b will relate to the how the customers reach to omotenashi and how they differentiate from each other, while research questions 2a and 2b will relate to hard and soft attributes and how the management decisions can impact future improvement in customer satisfaction.

------------
2. Comment #4 from Reviewer #3 & Comment #4 from Reviewer #5
I don't think there is nothing that the authors can do about it. I recommend the authors acknowledge it as a study limitation.

>>>Comment #4 from Reviewer #3
>>>"#4 - Method
    *  To provide a fair comparison, the two sets of texts should review the same hotels within a similar time period. The authors should provide this background information in order to demonstrate the fairness of comparing those two sets of texts

    *  Please report more information about the review samples, including time period, hotel and hotel attributes involved in this study and etc"

>>>Comment #4 from Reviewer #5
>>>"In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted? Are the same hotels extracted from both Ctrip and Tripadvisor? How many hotels are there? I believe different types of hotels would have generated different satisfaction level and perspectives. Please provide more details about these hotels."
------------

We added an extra layer to our research to overcome this limitation, although we admit that it's not fully encompassing the category or hotel type. We divided our datasets into price ranges. We chose the highest price available in each hotel for a single room and a single night. This way, even if most customers aren't staying in that room, we can categorize the hotels by their quality. For example, there's probably no capsule hotels with suite rooms that would offer very different experiences. This way we think that we can clearly distinguish cheaper hotels and hostels, from business hotels, and from Japanese style ryokan or resorts. Then we performed the analysis and updated the discussion that was already written by observing the differences in results across different prices. We also added a new subsection of discussion, where we analyze all the differences in one place. We also comment in limitations that it is true that some hotels priced similarly will offer different experiences (e.g. Western style resorts and Japanese style ryokan).

------------
3. Comment #6 from Reviewer #5
Among the four issues, it is the most critical one. Adjectives themselves cannot identify their associated attribute. I don't think "inspecting random samples" provides sufficient explanation. I recommend the authors run systematic analysis to examine the association between adjectives and nouns.

>>>Comment #6 from Reviewer #5
>>>"Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment". Can the authors explain further how this can be avoided in your data analysis?"
------------

We completely agree, and improved the paper by adding more steps to the methodology. We used the Stanford CoreNLP pipeline to perform dependency parsing and part of speech tagging to the collected reviews. We used the dependency parsing to find which words are connected to each other and how, and we used the part of speech tagging to verify that the connections were of adjectives and nouns. Then we incorporated those pairs in the frequency analysis and considered which attributes of the hotel the customers were referring to, and in which context. This method is not perfect, and we can only follow one connection per word, but it gives us a deeper insight into the factors that customers consider.

------------
4. Comment #7 from Reviewer #5
I am still confused with internal and external attributes. While the "location" of the hotels is an external attribute, "big" rooms, bathtubs, and bath facilities are internal attributes. Both the location of the hotel and the size of rooms and facilities cannot be changed once the construction of the hotel is completed. The authors may want to recategorise/rename them (e.g., tangibles/intangibles; soft/hard).
Look forward to it.

>>>Comment #7 from Reviewer #5
>>>"For the managerial and environmental keywords, what criteria were used for classifying these keywords? "
------------

We agree with your comment and decided to reclassify them as hard and soft attributes. Before we explain the new definitions.

=====================================

@@

------------
Section 3.3 contains a lot of misleading and confusing information:

1.   "In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures (Nielsen et al. 2017; Jones 2010; Gunaratne 2009; Hogan and Emler 1978)". This is a very strong sentence; can the authors show evident that these studies have say such a strong conclusion?
------------

We agree that it is a strong conclusion from the cited papers without context, so we have included more information from these papers, as well as a new citation on the origin of the term WEIRD (Western, educated, industrialized, rich, and democratic) populations. We expanded the description as follows:

"However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on WEIRD (Western, educated, industri- alized, rich, and democratic) populations that are culturally biased for the western world (Nielsen et al. 2017). The term WEIRD was coined by Henrich et al. (2010), who criticizes studies that assume that the subjects chosen from these populations are a representative sample of the rest of the world. This bias, albeit without the acronym, was discussed earlier about social psychol- ogy by Hogan and Emler (1978). Gunaratne (2009) pointed this bias out in discussions of globalization. At the same time, Nielsen et al. (2017) sampled papers on developmental psychology and statistically examined this bias. This western bias is pervasive in all kinds of social sciences, and tourism science is not an exception. For example, studies are easily performed in the language of the scientist doing surveys for the subjects. A great majority of tourist be- havior in history analysis has been performed with Western subjects and was thought to be universal until recent years."

@@

------------
2.   "both academic researchers and businesses have decided to study Chinese tourist behavior (Sun et al. 2017)." Chinese tourists' study did not start from 2017.
------------

We apologize for the ambiguity. The citation was not of the start of Chinese tourism studies, but instead it points to a review paper that analyzed this growth in studies by making a survey from 2001 to 2012 of such studies. In this paper Sun et al. (2017) find that a rapid growth has started since 2007 onwards, and that it's starkly different from the slow growth in previous years. We changed it in the main document as follows:

"Explaining this, Sun et al. (2017) analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism."

@@

------------
3.  "cross-cultural studies and analyses for Asian and Western tourists are scarce." And "One thing to note with the above cross-culture analyses is that they were performed before the year 2000." If the authors use Google scholar to search, I believe they could find hundred thousand of researches, this topic is not special or scarce at all. If the authors want to refer to Chinese and non-Chinese study, please do not generalize it as cross-cultural study. 
------------

We did not intend to generalize, it is a study between Asian and Western studies what we were referring to, so we reworded it in the document. While yes, cross-cultural studies in general aren't scarce, the specific case of Asian vs. Western, or even Chinese and non-Chinese, were very scarce. We reworded the text so that this is more obvious. Now, the topic at hand is special, considering its focus in the specific Japanese hospitality environment, which is even more scarcely researched. The particular combination that this paper offers is not found in previous research either.

We reworded as follows:

"[...] To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies specifically comparing Chinese and Western tourists. [...]

One thing to note with the above Asian vs. Western analyses is that they were performed before 2000, and that they are not Chinese specific, but study Asian people in general. Meanwhile, the current Chinese economy boom is making an increase in the influx of tourists of this nation. [...] However, our study of online reviews takes the data that the hotel customers uploaded themselves, making the analysis unique in the exploring of their behavior in comparison with Western tourists, as well as studying them in the specific environment of high-level hospitality in Japan and observing hard factors that are not considered in most other studies."

### 2020-10-07 3_review-responses/V1_review_responses/Reviewer #1 Response.txt

"""
1. Machine learning

While this manuscript contains machine learning in its title, there is no major discussion about it. What is machine learning? How do the authors define it? Is data mining part of machine learning? If so, how so? Why is important or useful to use machine learning particularly for this study? What do the authors want to achieve with machine learning?  
"""

Machine learning and data mining often overlap, which is why we had an oversight in defining both of them and explaining their differences. In a journal about Information Technology, we assumed it was general knowledge, but we added it for consistency and for a more widespread reader understanding. In the section previously titled 3.4 "Data mining, knowledge discovery and sentiment analysis", thus renamed 3.4 "Data mining, machine learning, knowledge discovery and sentiment analysis" we introduced two paragraphs defining machine learning, its importance of use for analyzing larger samples, and what we can achieve with it. However the manuscript title changed from another reviewers request.

"""
Also, the manuscript can be improved by justifying and elaborating on the necessity of a large sample. Why is it so important about analysing a large sample? What problem did a "small" sample used in existing literature cause? 
I recommend the authors to prepare a section dedicating to these questions.
"""

@@

In regards to the sample size, a paragraph in previously 3.2, now section 3.3 "Chinese and Western tourist behavior" already describes the importance of these bigger samples. We added a bit of text to expand on this importance.

> "Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable. We can see that depending on the study and the design of questionnaires, as well as the destinations, the results can vary greatly. Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other. However, since our study uses data mining, the definition of each subject or factor is left for the hotel customers to decide en masse via their reviews (instead of being defined by the questionnaire). This means that the factors will be selected through statistical methods alone. This opened opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves. This large variety of opinions in a big sample, added to the automatic findings of statistical text analysis methods, is what gives an advantage to our study in comparison to others with smaller samples. In addition, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature."

"""
2. Theoretical discussion on culture
I also recommend the authors to develop the story on culture with theoretical perspectives. Why would Westerners show different preferences from Chinese? Why do Westerners value soft attributes (or managerial factors) like staff more while Chinese value hard attributes (or environmental factors) like size? Why do both Westerners and Chinese share dissatisfactory attributes while they show different satisfactory attributes (see Table 6)? While this study did not measure "culture" per se, I believe the authors can find theoretical explanations.
"""

### 2020-10-07 3_review-responses/V1_review_responses/Reviewer #3 Response.txt

Reviewer #3 Response

Thank you for your review observations. I will quote each observation and respond to it while indicating my corrections in the text.
Aside from these corrections, we also performed a general grammar check and proofread to the new manuscript, including unchanged sections. Because of comments by reviewers, we redid the experiment with more balanced data, so the results shown are different in their quantitative values. However, our conclusions and hypothesis testing remained largely unchanged by this. We also added a new research rationale and focus, which meant new hypotheses were added to the manuscript. The new manuscript focuses on how these populations interact with the high-standard spirit of Japanese hospitality and service called Omotenashi. In this environment, will the cultural differences be strong enough that their satisfaction stems from different factors?, or will both populations be largely satisfied by service and staff related terms?

"""
#1 - Research rationale
The authors mentioned "Up until recently, most studies in tourist behavior have been biased for the Western world". Yet, to the best of my knowledge, there are fruitful studies examined Chinese consumers' hotel booking behavior

I searched and found that several similar studies have already been published recently like:
  Francesco, G., & Roberta, G. (2019). Cross-country analysis of perception and emphasis of hotel attributes. Tourism Management, 74, 24-42.
  Huang, J. (2017). The dining experience of Beijing Roast Duck: A comparative study of the Chinese and English online consumer reviews. International Journal of Hospitality Management, 66, 117-129.
  Jia, S. S. (2020). Motivation and satisfaction of Chinese and US tourists in restaurants: A cross-cultural text mining of online reviews. Tourism Management, 78, 104071.

The authors are encouraged to review and indicate the existence of the above articles. To highlight the uniqueness of this work, the authors can highlight how the current study differs from other published works in terms of "research focus", "methodological approach", "study context" or/and "data size"
"""

@@

We added a paragraph in the beginning of our introduction, modified the abstract, and added the literature review in this context in previously 3.2, now section 3.3 Chinese and Western tourist behavior. We also changed the title to emphasize this context as well.

Because of the change in rationale, new hypotheses were added as well. The main problem in our refocused paper is: In such a high-standard hospitality environment, will the cultural backgrounds react similarly or differently to them? Will they both be satisfied more with hospitality and service related topics than with other topics, or will they ignore this environment?

We found that Chinese tourists don't react as positively to this hospitality as Westerners did. We have two theories which we discussed in section 7. One is that they don't have the same expectations. Getting what they don't expect leads to less satisfaction than if they were expecting it. Another theory is that the language barrier poses an obstacle to the enjoyment of this hospitality.

"""
#2 - Research objectives
  Section 2 shows that the objective of this study is to determine the difference in preferences between Chinese- and English-speaking customers of Japanese hotels using text-mining techniques. Yet, according to my review, this study solely examines what English- and Chinese-speaking customers concern most when they evaluate Japanese hotels

  I can accept the assertion that the findings can reflect the differences in factors driving satisfaction and dissatisfaction between Chinese- and English-speaking customers. But the findings cannot reflect their preferences
"""

@@

In a previous version of our manuscript, we had another reviewer point out that "satisfaction and dissatisfaction factors" was a long way to say preferences, which is why we had it corrected this way. Based on this more recent review, however, we happily reverted it to the previous terminology. This is reflected in the manuscript and title. We also modified the research objective to match the new research rationale that was encouraged in a previous point.

"""
#3 - Literature review
  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them.

  For Section 3.2, the authors may consider reviewing more cross-country studies and presenting the findings in a tabular format (with the column showing study topic, industry, samples' nationality …) This comparison table shall be helpful for the authors to justify if the research gaps truly exist
"""

@@

As to the first point, we believe there is always a necessity in science to re-examine and avoid making assumptions. In addition to this thought, other reviewers have found the hypotheses helpful in the flow of the manuscript, so we decide to keep them as part of the manuscript. As part of the rationale change, we also added new hypotheses.

For the second point, we agree that adding literature was necessary as per a previous point. We also agree that displaying them such a table would give a helpful overview of the current research in this topic for our paper and have included it in the previously 3.2, now section 3.3.

"""
#4 - Method
  To provide a fair comparison, the two sets of texts should review the same hotels within a similar time period. The authors should provide this background information in order to demonstrate the fairness of comparing those two sets of texts

  Please report more information about the review samples, including time period, hotel and hotel attributes involved in this study and etc
"""

@@

We added this paragraph to the Data collection section:

"However, in order to make the data and comparisons we draw from each of these datasets fair, we filtered both databases to only contain reviews from hotels that were in both datasets, using their English names to do a search match. We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges. After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{580}, and that the common date range for reviews was from July 2014 to July 2017. We also found that the price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve. Within this range, from \textit{Ctrip} there was \num[group-separator={,}]{49561} reviews comprised of \num[group-separator={,}]{105076} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41611} reviews comprised of \num[group-separator={,}]{352022} sentences.

We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general."

"""
#5 - Discussions and Conclusions
  Regarding the discussion part, the authors discussed the differences (in sections 7.1 and 7.2) and the similarities (in section 7.3 and 7.4) of Western and Chinese consumers' satisfaction and dissatisfaction factors.  However, the authors discussed the difference in section 7.5 again. Also, the smell of Tobacco was already mentioned in the section 7.2 ("the most common complaint regarding cleanliness was about the carpet, followed by complaints about stains, and cigarette stench in the curtains"). This is a little bit confusing, and I kindly suggest the authors to re-organize the discussion part

  The manuscript does not include much discussions about its theoretical contributions. Again, how what new knowledge was brought by this study? Any contrasting findings were found?
"""

### 2020-10-07 3_review-responses/V1_review_responses/Reviewer #5 Response.txt

Thank you for your review observations. I will quote each observation and respond to it while indicating my corrections in the text.
Aside from these corrections, we also performed a general grammar check and proofread to the new manuscript, including unchanged sections. Because of comments by reviewers, we redid the experiment with more balanced data, so the results shown are different in their quantitative values. However, our conclusions and hypothesis testing remained largely unchanged by this. We also added a new research rationale and focus, which meant new hypotheses were added to the manuscript. The new manuscript focuses on how these populations interact with the high-standard spirit of Japanese hospitality and service called Omotenashi. In this environment, will the cultural differences be strong enough that their satisfaction stems from different factors?, or will both populations be largely satisfied by service and staff related terms?

"""
This study used Ctrip as the data base. However, majority users of Ctrip is Mainland Chinese, but Chinese-speaking tourists can also be Taiwanese, Malaysian Chinese, Singaporean Chinese and Hong Konger too. Therefore I suggest the authors change the term Chinese-speaking tourists to Mainland Chinese tourists.
"""

Thanks for pointing this information out. We pointed this out in the text.

"""
In literature review, the authors listed three hypothesis relating to Chinese and English speaking tourists in 3.1 and then a separate section 3.2 to explain the difference between Chinese and Western tourists. I would suggest the authors combine these two sections so as to give a more comprehensive view on the setting of the three hypothesis.
"""

@@

We respectfully disagree with this suggestion since the content of section 3.1 and 3.2 are very different. While 3.1 sets the premise of differences in customer satisfaction and the reasoning behind them existing, 3.2 discusses previous literature on specific behaviors and cultures of each kind of tourist. Since we added a new section 3.1, these two sections are now 3.2 and 3.3 respectively.

"""In formular (1), what are alpha, x and y?"""

We added a description of the formula to the manuscript, as well as a short description of the SVM algorithm to make it more understandable.

"""
In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted? Are the same hotels extracted from both Ctrip and Tripadvisor? How many hotels are there? I believe different types of hotels would have generated different satisfaction level and perspectives. Please provide more details about these hotels.
"""

@@

We added this paragraph to the Data collection section:

"However, in order to make the data and comparisons we draw from each of these datasets fair, we filtered both databases to only contain reviews from hotels that were in both datasets, using their English names to do a search match. We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges. After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{580}, and that the common date range for reviews was from July 2014 to July 2017. We also found that the price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve. Within this range, from \textit{Ctrip} there was \num[group-separator={,}]{49561} reviews comprised of \num[group-separator={,}]{105076} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41611} reviews comprised of \num[group-separator={,}]{352022} sentences.

We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general."

"""
In Table 2, I am quite surprise to see that the last item "Chinese person" can be the top keywords with only 16 occurrences. Can the authors explain why there are so few negative Chinese keywords?
"""

@@

Since we repeated the experiment, the frequencies have changed, however this keyword still only has 16 occurrences. The lack of negative keywords comes from a peculiarity of the Chinese reviews from Ctrip. Most of the reviews point out the positive extensively, while only a few sentences are negative. It's a limitation of our paper that the negative keywords depend on the sample taken at the beginning, since we could not label more manually at the time.

"""
Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment". Can the authors explain further how this can be avoided in your data analysis?
"""

@@

One thing to note is that using SVM, we labeled sentences as positive or negative, so negative usage of the word when counting the frequencies is negligible. In addition to this, we also had the same question when we saw our results the first time, and took a small sample to observe the usage of the word. However we didn't deem it appropriate in the text at first, but with this comment and thinking it over once again, we have added the next paragraph to the manuscript:

>"From these two first ranking keywords (“big” and “clean”), we can assert
that room quality is the most critical satisfaction factor for Chinese customers. However, the word “big” is widespread in the language and could be used in different contexts to point out positive and negative aspects. Since we are interested in how the word is a keyword of positive sentences, we took a small sample of the positively classified sentences that contained the word “big” in Chinese. A team of Chinese speaking lab members then pointed out the usage of the word. Generally speaking, it was used for the spaciousness of rooms, bathtubs, and communal bath facilities."

"""
For the managerial and environmental keywords, what criteria were used for classifying these keywords? 
"""

@@

We explain the difference between managerial and environmental factors in different sections of the manuscript. However, since it might still be unclear, we specified the method for classifying the keywords in the Results section, adding the following text:

> "We manually labeled the top
625 keywords of each language into either managerial or environmental by considering how the word would be used when writing a review. If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it managerial. If the word is describing factors that are unchangeable by the staff or management, we consider them environmental. The interpretation of these keywords is shown in the Tables 8 and 9."

We also added the tables that were previously in the appendix clearing this issue into the main text for readability.

"""
Editorial issues
The Appendix is actually part of the manuscript. This manuscript contains too many Tables. First some was mentioned in the manuscript but appeared in Appendix. For example line 306, Table 7 and Section B was mentioned. What is Section B?  Please move all relevant tables to the manuscript but not in Appendix. I would suggest the authors to consider to either combine some of them or not to mention them in the manuscript. 
Besides, the numbering of the tables was not in sequence in the manuscript. Line 360, after Table 3 and 4, it suddenly jumps to Table 10.
"""

### 2020-10-07 2_revisions/V2_ITT_first revision/itt-emotion_V2 (1).tex
restore png to git from lfs, permissions

\begin{figure}[bp]
\centering
\includegraphics[width=\textwidth]{emotion-method-overview_V2.png}
\caption{Overview of the methodology to quantitatively rank satisfaction factors.}
\label{fig:method-overview}
\end{figure}

@@

In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, confirming our hypothesis \ref{hyp:omotenashi_en}. However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction. As such, our hypothesis \ref{hyp:omotenashi_zh} is rejected. Since both cultures have a different reaction to this environment of hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed. From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{Omotenashi}. One theory is that they are not being treated well enough, and this environment is not compatible with them because of language or culture barriers. The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way. We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.

We obtained values ranging from 0.176 to 0.257 in satisfaction lists and from 0.128 to 0.176 in dissatisfaction lists at different cutoff points. These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the satisfaction and dissatisfaction factors of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:diff_all}. We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers. We found that from the four words that were common amongst both groups (``clean", ``recommend," ``subway," and ``price"). When these shared terms were isolated, both lists were almost identical at the cutoff point of 20 words. This resulted in an RBO ranging from 0.906 to 1.0. This means our hypothesis \ref{hyp:diff_com} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.

@@

In contrast, environmental attributes only make for a smaller portion of the factors (40\% of the top 10 satisfaction keywords). In the case of Chinese customer satisfaction, the top of the list was managerial (30\% of the top 10 words), and a more significant portion, although lower in its ranking, was environmental (40\%). For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial, while the other 28.6\% were environmental. We discussed how these distributions in managerial or environmental factors having priorities in either population could lead to different management strategies. One possible approach is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number. They are less satisfied with managerial factors but have an identifiable method of improving satisfaction by lessening language barriers and providing breakfast. Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free. With this strategy, we favor ``long-haul'' Western tourists who spend almost half of their budget on hotels. While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns. The reason for this being that Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased. In this paper, we provide results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan, and we can observe their stark differences and shared attributes.

>>>>

\begin{figure}[bp]
\centering
\includegraphics[width=\textwidth]{emotion-method-overview_V2.png}
\caption{Overview of the methodology.}
\label{fig:method-overview}
\end{figure}

@@

In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, confirming our hypothesis \ref{hyp:omotenashi_en}. However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction. As such, our hypothesis \ref{hyp:omotenashi_zh} is rejected. Since both cultures have a different reaction to this environment of hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed.

We obtained values ranging from 0.176 to 0.257 in satisfaction lists and from 0.128 to 0.176 in dissatisfaction lists at different cutoff points. These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the satisfaction and dissatisfaction factors of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:diff_all}.

We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers. We found that from the four words that were common amongst both groups (``clean", ``recommend," ``subway," and ``price"). When these shared terms were isolated, both lists were almost identical at the cutoff point of 20 words. This resulted in an RBO ranging from 0.906 to 1.0. This means our hypothesis \ref{hyp:diff_com} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.

@@

In contrast, environmental attributes only make for a smaller portion of the factors (40\% of the top 10 satisfaction keywords). In the case of Chinese customer satisfaction, the top of the list was managerial (30\% of the top 10 words), and a more significant portion, although lower in its ranking, was environmental (40\%). For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial, while the other 28.6\% were environmental. Our results and discussion can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan, and we can observe their stark differences and shared attributes.
